---
title: "Experimental TidyTuesday"
output: github_document
bibliography: packages.bib
nocite: "@*"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = "center", cache = FALSE)

knitr::write_bib(renv::dependencies()$Package, file = "packages.bib") # Line to write the all packages references in a file called packages.bib
```


This repo will host the code and figures from students of the experimental biology course at from EAFIT university, who are exploring a [TidyTuesday](https://github.com/rfordatascience/tidytuesday) dataset as a course activity. Each student will inquire the selected dataset, and with [tidyverse](https://www.tidyverse.org) tools will aim to solve its question.

This activity looks forward to the students to familiarize with git, github and tidyverse tools, having a question as a central axis.

The following code chunk have the essential libraries for the subsequent code.
```{r libraries, warning=FALSE, message=FALSE}
library(tidyverse)
library(tidytuesdayR)

tuesdaydata <- tt_load("2021-10-19")

pumpkins <- tuesdaydata$pumpkins
```


## Alexandra

```{r Alexandra}

```


## Amalia

```{r Amalia}

```

## Andrés

```{r Andres}

```

## Manuela

```{r Manuela}

```

## Maria José

```{r MariaJose}

```

## Pablo

```{r Pablo}

```

## Susana

```{r Susana}

```

# References